\pkg{fitdistrplus}: An \proglang{R} Package for Fitting Distributions

### 2013-05-17 JSS/fitdistrplus/paper2JSS.Rnw
minor corrections
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/riskassessment@251 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<danish.mme.pareto, echo=TRUE, fig=FALSE>>=
library("actuar")
fdanish.P.MLE <- fitdist(danishuni$Loss, "pareto", 
start=c(shape=10, scale=10), lower=2+1e-6, upper=Inf)
memp <- function(x, order) sum(x^order)/length(x)
fdanish.P.MME <- fitdist(danishuni$Loss, "pareto", method="mme", 
order=1:2, memp="memp", start=c(shape=10, scale=10), 
lower=c(2+1e-6,2+1e-6), upper=c(Inf,Inf))
cdfcomp(list(fdanish.P.MLE, fdanish.P.MME), 
legend=c("Pareto MLE", "Pareto MME"), 
main="Fitting a Pareto distribution", xlogscale=TRUE, datapch=".")
gofstat(list(fdanish.ln.MLE, fdanish.P.MLE, 
fdanish.ln.MME, fdanish.P.MME),
fitnames = c("lnorm.mle","Pareto.mle","lnorm.mle","Pareto.mme"))
@

>>>>

<<danish.mme.pareto, echo=TRUE, fig=FALSE>>=
library("actuar")
fdanish.P.MLE <- fitdist(danishuni$Loss, "pareto", 
start=c(shape=10, scale=10), lower=2+1e-6, upper=Inf)
memp <- function(x, order) sum(x^order)/length(x)
fdanish.P.MME <- fitdist(danishuni$Loss, "pareto", method="mme", 
order=1:2, memp="memp", start=c(shape=10, scale=10), 
lower=c(2+1e-6,2+1e-6), upper=c(Inf,Inf))
cdfcomp(list(fdanish.P.MLE, fdanish.P.MME), 
legend=c("Pareto MLE", "Pareto MME"), 
main="Fitting a Pareto distribution", xlogscale=TRUE, datapch=".")
gofstat(list(fdanish.ln.MLE, fdanish.P.MLE, 
fdanish.ln.MME, fdanish.P.MME),
fitnames = c("lnorm.mle","Pareto.mle","lnorm.mme","Pareto.mme"))
@
